Goes Here

### 2012-07-30 paper.tex
Copy more text from proposal

\section{Introduction}
3D printing has the potential to dramatically reduce the required time and cost of
fabricating custom materials and objects. In particular, it allows the fabrication of materials with complex internal
structures that are difficult or impossible to manufacture with other technologies. Additive manufacturing could be
much more widely adopted and easier to use, given a high-fidelity translation from specifications of objects defined
in terms of their mechanical, optical, and appearance properties to output-device-specific computer
programs that produce the best possible approximation of these digital objects. However, this is still one of
the most important unsolved problems in digital direct manufacturing. Due to its combinatorial nature, this
problem becomes more and more challenging as the range of different printable materials increases. This paper
aims to provide an abstraction mechanism and a software framework for translating specifications to fabrication
instructions. It is possible to design a computationally efficient and general process for translating virtual objects
with desired mechanical, electrical, optical, and appearance properties into composite printable materials.
We will achieve this goal through a reduction-optimization-simulation approach.
\section{Previous Work}

@@

searches through the space of all possible device outputs
obtained by the simulator to nd the one that best reproduces

@@

has NM dimensions. To overcome this problem, we reduce

@@

partial solutions that yield similar output properties [1], avoiding combinatorial explosion of the search space.

@@

\subsection{Simulation}
Another key step in the process of converting abstractions to physical output is being able to
simulate what an output device is going to generate given a well-defined input. A simulation allows the
user to preview how the output will look and behave. This simulation is a generalization of the print-preview function
available in word processing applications. As physical output generation might be costly or time-consuming, it
is extremely beneficial for users to be able to preview the output and make immediate changes to the design. That
means that the simulation must accurately predict the output. It's necessary to develop very efficient and accurate rendering
and finite element simulation packages. Since we run the simulation multiple times within the optimization method
we can cache and reuse partial simulation results, speeding up the evaluation process at least 10-100 times. Furthermore,
we will ensure that the simulation is accurate by measuring properties of the printing materials and using
these measurements to estimate the parameters of data-driven material models (e.g., for elasticity, reflectance).
\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
\subsection{Textured Model}
Input: a textured 3D model and
	measured Albedo of print material.

>>>>

\section{Introduction}
3D printing has the potential to dramatically reduce the required time and cost of
fabricating custom materials and objects. In particular, it allows the fabrication of materials with complex internal
structures that are difficult or impossible to manufacture with other technologies. Additive manufacturing could be
much more widely adopted and easier to use, given a high-fidelity translation from specifications of objects defined
in terms of their mechanical, optical, and appearance properties to output-device-specific computer
programs that produce the best possible approximation of these digital objects. However, this is still one of
the most important unsolved problems in digital direct manufacturing. Due to its combinatorial nature, this
problem becomes more and more challenging as the range of different printable materials increases. This paper
aims to provide an abstraction mechanism and a software framework for translating specifications to fabrication
instructions. It is possible to design a computationally efficient and general process for translating virtual objects
with desired mechanical, electrical, optical, and appearance properties into composite printable materials.
We will achieve this goal through a reduction-optimization-simulation approach.
\section{Previous Work}
\subsection{Simulation of the Appearance of Ink Combinations}
[20] built a system
for the measurement of Bidirectional Reflectance Distribution Functions (BRDFs) and were able
to acquire BRDFs for both single-layer and multi-layer ink printouts (e.g., an ink covered by a
varnish layer). They then acquired a database of many different combinations of ink layers (up to
seven layer combinations were considered). However, they did not develop a method to simulate
the appearance of arbitrary ink layers. They were able to interpolate the appearance by spatially
multiplexing small tiles of different base combinations. By linearity of light transport, the simulation
of the combined appearance was reduced to linear combinations of the base BRDFs. 
simulation method for the appearance of translucent materials [59]. 
They
built a measurement system for estimating multiple-scattering in homogeneous material slabs. They
measured both transmission and refection for a set of base materials used by the OBJET Connex
multi-material printer. 
Using these measurements, our simulations framework was able to predict
diffuse reflections and transmissions in multi-layered translucent objects composed of base material
layers.
In the proposed research, we will extend these methods to cover the complete appearance of
volumetric materials that accounts for both directly reflected light and light scattering within the
material volume. 
We will use efficient simulation methods that allows us to simulate the appearance
of complex structures composed from these base materials. We developed an initial framework for
simulating behavior of multi-layered materials, where each layer is a homogeneous base material.
Then we extend this simulation to materials in which each voxel is made of a different measured
material. Since this general simulation is expensive and requires path-tracing algorithms, we used
algorithms that are based on fast numerical integration of our low-dimensional representations
and the use of pre-computation, similar to pre-computed light transport approaches [63].
\subsection{Simulation of Deformation Behavior}
In previous work, the problem
of modeling and simulating soft materials and their deformation behavior [22, 60].
In order to accurately model deformation behaviors they built a system that allowed measuring how
a given material deforms subject to a variety of external forces. 
The system used an automated
robot arm to apply desired forces and a vision subsystem to measure corresponding surface deformations.
We modeled deformation behavior of a material using a stress-strain relationship. Since
the deformation behavior of many of our materials was non-linear, we developed a model that could
accurately represent this behavior and that was also easy to fit to the surface measurements. In
our model, the stress-strain relationship was represented as a collection of linear stress-strain relationships.
We used a properly chosen function to interpolate between these linear relationships
and obtain a non-linear model. Using this system and model we could accurately measure material
deformation of a collection of materials produced by a multi-material printer and fit these observation
to the stress-strain model. Then, using this material model within a Finite Element Method
we could accurately simulate behavior of any shape made from a composite of measured materials.
In the proposed research, we would like to address the shortcomings of our current measurement
and models. First, our current approach handles only elastic material deformation. We would like to
extend our current data-driven model to viscoelastic materials. In fact, most real materials exhibit
this property, which is characterized by hysteresis (or material memory). For these materials, it is
not possible to predict the behavior of a material only based on the currently applied stress. One also
has to know the history (or the sequence) of applied stress values to accurately simulate material
behavior. In order to determine the material model one has to measure the so called hysteresis
loops in the stress-strain space (as opposed to a single stress-strain curve for elastic materials). The
hysteresis loop is the result of the damping effect which causes the material to behave differently
depending whether stress is applied or removed as some of the energy is dissipated within the
material into heat. Additional advantage of using this material model is that it will allow us to
handle dynamic material deformations.

In order to measure viscoelastic material properties, we will need to modify our current measurement
system and procedures. We will use repeatable, time-coded measurements to estimate
Figure 5: From left to right: Force-and-deformation capture of a non-linear heterogeneous pillow;
synthesized deformation with fitted material parameters; and interactive deformation synthesized
with our soft tissue modeling technique using scattered data interpolation [60].

We will also use faster resonating actuators and high-speed
camera systems to track material deformations at high frame rates. Furthermore, we plan to track
the whole material volume rather than the outer material surface. This is possible since we can
print materials in clear color as well. Thus small color-coded markers can be easily embedded into
the material structure. These markers can be tracked in 3D using a multi-camera system.

@@

searches through the space of possible device inputs
to find the one that best reproduces

@@

has $N^M$ dimensions. To overcome this problem, we reduce

@@

partial solutions that yield similar output properties, avoiding combinatorial explosion of the search space.

@@

\subsection{Simulation}
Another key step in the process of converting abstractions to physical output is being able to
simulate what an output device is going to generate given a well-defined input. 
A simulation allows the user to preview how the output will look and behave. 
This simulation is a generalization of the print-preview function
available in word processing applications.
As physical output generation might be costly or time-consuming, 
it is extremely beneficial for users to be able to preview the output and make immediate changes to the design.
That means that the simulation must accurately predict the output. 
It's necessary to develop very efficient and accurate rendering
and finite element simulation packages. Since we run the simulation multiple times within the optimization method
we can cache and reuse partial simulation results, speeding up the evaluation process at least 10-100 times.
Furthermore, we will ensure that the simulation is accurate by measuring properties of the printing materials and using
these measurements to estimate the parameters of data-driven material models (e.g., for elasticity, reflectance).
\section{Programming with Our API}

\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
\subsection{Textured Model}
Input: a textured 3D model and
	measured Albedo of print material.
